### 2019-03-12 papers/journal/encoding.tex
made ambiguou claim

\input{satqbf-table}
%
The table~\ref{tab:satqbf-graph}, shows the search results of this encoding for the universal condition with 5 nodes and 3-connected graphs. 
%
The SMT extended version was not able to scale it to the desired results and either timed-out (T/O) or ran out of memory (M/O).
%
This can be due to the fact that directly translating a quantified formula into a quantifier-free  by introducing a vector of variables for each boolean possibility will blow up the size of the formula and may not be solvable by a SAT solver.

>>>>

\input{satqbf-table}
%
The table~\ref{tab:satqbf-graph}, shows the search results of this encoding for the universal condition with 5 nodes and 3-connected graphs. 
%
The SMT extended version was not able to scale it to the desired results and either timed-out (T/O) or ran out of memory (M/O).
%
This can be due to the fact that directly translating a quantified formula into a quantifier-free  by introducing a vector of variables for each boolean possibility will blow up the size of the formula and may not be solvable by a solver.
